---
title: "Week 9"
author: "Jaymeen Gandhi"
date: "April 4, 2020"
output:
  word_document: default
  html_document: default
---

```{r}
require(tidyverse)
```

```{r}
projects = read_csv('C:/Users/jayme/Downloads/projects.csv')
projects = projects %>% arrange(desc(comments))
projects = projects %>% filter(comments<10000)
projects
```

```{r}
f = comments ~ duration + goal + description.length
```

```{r}
projects %>% summarise(mean(comments),var(comments))
```

##Since the var is very high than mean we can say that the distribution is overspread. So this model will be quasi poisson.
##If the variance and mean are equal than use poissons.

```{r}
model = glm(f,data = projects,family = quasipoisson)
summary(model)
```

## Since this model does nor have any r-squared value we have to check whether this model is a good fit for prediction or no.

##We will see that as follows
```{r}
require(broom)

glance(model) %>% summarise(pseudoR2=1-deviance/null.deviance)
```

##Now we will see model prediction and evaluate that prediction

```{r}
set.seed(1234)
training_data = projects %>% sample_frac(size = 0.7)
testing_data = anti_join(projects,training_data, by= 'id')
```

```{r}
model_l = glm(f,data = training_data,family = gaussian)
model_p= glm(f,data = training_data,family = poisson)
model_qp = glm(f,data = training_data, family = quasipoisson)

models = list(model_l,model_p,model_qp)


```

```{r}
map_dfr(models, ~glance(.x) %>% summarise(pseudoR2=1-deviance/null.deviance))
```


########## GAM Models ###########

```{r}
#install.packages('mgcv')
require(mgcv)
require(modelr)
```
```{r}
mtcars %>% head()
```

```{r}
gam_model = gam(mpg ~ s(disp), data = mtcars)
lm_model = lm(mpg ~ disp , data = mtcars)
lm_t_model = lm(mpg~I(1/disp^2),data = mtcars)

models=list(gam_model,lm_model,lm_t_model)

(rsquared=map_dbl(models,~rsquare(.x,mtcars)))
```

```{r}
mtcars = mtcars %>% mutate(id = row_number())
set.seed(1234)
training_data = mtcars %>% sample_frac(size = 0.7)
testing_data = anti_join(mtcars,training_data, by= 'id')
```

```{r}
gam_model = gam(mpg ~ s(disp), data = training_data)
lm_model = lm(mpg ~ disp , data = training_data)
lm_t_model = lm(mpg~I(1/disp^2),data = training_data)

models=list(gam_model,lm_model,lm_t_model)

(rmses = map_dbl(models,~rmse(.x,testing_data)))
```

```{r}
tibble(model=c("gam_model","lm_model","lm_t_model"),rsquared,rmses) %>% mutate_if(is.numeric,~round(.x, 2))
```







